### 2021-12-27 paper.tex
intorduction start

\documentclass[12pt,titlepage,a4paper]{article}
\usepackage[utf8]{inputenc}
\usepackage{amsmath}
\usepackage{amsfonts}
\usepackage{babel}
\usepackage{graphicx}
\usepackage{amssymb}
\usepackage{amsthm}

@@

\pagebreak
\section{Task 2 Semantic Decoding}
Semantic decoding translates sentences into the set of sematic concepts, which consists of 2 parts: intent (or dialog act type) and sematic slots and values. For instance the sentence "I want to book a flight to Berlin" can be translated into the intent "book" and the slots "flight" and "to" with the value "Berlin"($book(flight, to(Berlin))$).

@@

Macro average can be much lower than a weighted average, because there can be a lot of rare classes with few instances which were not predicted or predicted wrongly while there are not so many classes with a lot of instances, which are therefore predicted correctly.
%===========================================================
\section{Task 3}
Focus tracker accumulates evidence of a changing state over the course of the dialogue. Let's define for methods and goal components $c \in V_c$ (all possible slot values) the quantity denoting that a slot(method) is not present in turn $t$:

>>>>

\documentclass[12pt,titlepage,a4paper]{article}
\usepackage[utf8]{inputenc}
\usepackage{amsmath}
\usepackage{amsfonts}
\usepackage{babel}
\usepackage{graphicx}
\usepackage{amssymb}
\usepackage{amsthm}
\usepackage{hyphenat}

@@

\pagebreak
\section{Spoken Dialog System}
A spoken dialogue system is a computer system that enables human computer interaction where primary input is speech. Examples of such systems are voice assistants, chatbots, and conversational interfaces (Siri, Alexa, Google Home, etc.). \par

A good spoken dialogue system has the following properties: understands the user, decides what to say back, conducts a conversation beyond simple vo\-ice commands or question answering. 
In this overview we will be considering a goal-oriented systems (the ones which are targeted to accomplish a goal in the context of a task - to book a restaurant for ex.). In this case the scope of the conversation is usually limited to a specific domain - a database contating all knowledge about the topic. Such database is called an ontology.
\pagebreak
\section{Task 2 Semantic Decoding}
Semantic decoding translates sentences into the set of sematic concepts, which consists of 2 parts: intent (or dialog act type) and sematic slots and values. For instance the sentence "I want to book a flight to Berlin" can be translated into the intent "book" and the slots "flight" and "to" with the value "Berlin"($book(flight, to(Berlin))$).

@@

Macro average can be much lower than a weighted average, because there can be a lot of rare classes with few instances which were not predicted or predicted wrongly while there are not so many classes with a lot of instances, which are therefore predicted correctly.

Let's have a look on how the tags are recognised after training. 
\begin{center}
    \resizebox{\textwidth}{!}{
    \begin{tabular}{ c c c c c c c c c c c c c }
        & find & a & flight & from & tampa & to & montreal & by & way & of & new & york
        \\ 
        predicted & O & O & O & O & B-fromloc.city\_name & O & B-toloc.city\_name & O & O & O & B-fromloc.city\_name & I-fromloc.city\_name
        \\ 
        true & O & O & O & O & B-fromloc.city\_name & O & B-toloc.city\_name & O & O & O & B-stoploc.city\_name & I-stoploc.city\_name \\  
    \end{tabular}}
\end{center}

We can fix it by adding words "with a stop in".
\begin{center}
    \resizebox{\textwidth}{!}{
    \begin{tabular}{ c c c c c c c c c c c c c c}
        & find & a & flight & from & tampa & to & montreal & with & a & stop & in & new & york
        \\ 
        predicted & O & O & O & O & B-fromloc.city\_name & O & B-toloc.city\_name & O & O & O & O & B-stoploc.city\_name & I-stoploc.city\_name  
    \end{tabular}}
\end{center}

There are also many instances when the state name is recognized as a city name. 
\begin{center}
    \resizebox{\textwidth}{!}{
    \begin{tabular}{ c c c c c c c c c c c}
        & please & find & a & flight & from & las & vegas & to & michigan
        \\ 
        predicted & O & O & O & O & O & B-fromloc.city\_name & I-fromloc.city\_name &  O & B-toloc.city\_name
        \\ 
        true & O & O & O & O & O & B-fromloc.city\_name & I-fromloc.city\_name &  O & B-toloc.state\_name \\  
    \end{tabular}}
\end{center}

Arrival time can be mistaken with departing time:
\begin{center}
    \scalebox{0.7}{
    \begin{tabular}{ c c c c c}
        Sentence & True & Predicted & Changes & New prediction\\
        i &O&O & i & O\\
        would &O&O & would & O\\
        like  &O&O & like & O\\
        to &O& O & to & O\\
        return &O& O & fly& O\\
        from &O& O & around & B-depart\_time.time\_relative\\
        chicago &B-fromloc.city\_name& B-fromloc.city\_name & 7 & B-depart\_time.time\\
        around &B-depart\_time.time\_relative& B-depart\_time.time\_relative & in & O\\
        7 &B-depart\_time.time& B-depart\_time.time & the & O\\
        pm &I-depart\_time.time& I-arrive\_time.time & evening & B-depart\_time.period\_of\_day\\
        to &O& O & from & O\\
        kansas  &B-toloc.city\_name& B-toloc.city\_name & chicago & B-fromloc.city\_name\\
        city &I-toloc.city\_name& I-toloc.city\_name & to & O \\
        &&&kansas & B-toloc.city\_name\\
        &&& city & I-toloc.city\_name\\
    \end{tabular}}
\end{center}

We can fix wrongly recognized "pm" by adding - in the evening.
%===========================================================
\section{Task 3}
Focus tracker accumulates evidence of a changing state over the course of the dialogue. Let's define for methods and goal components $c \in V_c$ (all possible slot values) the quantity denoting that a slot(method) is not present in turn $t$:
